---
title: "People"
---

This page describes the people who are involved with Field Day.

## Organizing Committee

- Woody Brem K3YV
- Rick Gilmore W3TM
- Eric Prescott W3EDP

## Special Roles

```{r}
#| echo: false
survey <- readr::read_csv(file.path("csv", "clean_narc-fd-2026-survey.csv"), show_col_types = FALSE)
```

Modify file based on email conversations that aren't captured in the data.

```{r}
#| echo: false
survey <- dplyr::mutate(survey, stations = NA)
survey <- dplyr::add_row(
  survey,
  callsign = "N3LI",
  name = "Mike Coslo",
  clean_up = TRUE,
  stations = TRUE
)
survey <- dplyr::add_row(
  survey,
  callsign = "W3SWL",
  name = "Brett Saylor",
  clean_up = TRUE,
  stations = TRUE
)

survey$stations[survey$callsign == "K3YV"] <- TRUE
survey$stations[survey$callsign == "W3EDP"] <- TRUE
survey$stations[survey$callsign == "W3TM"] <- TRUE
survey$stations[survey$callsign == "KD3CCO"] <- TRUE
survey$stations[survey$callsign == "KC3MVL"] <- TRUE

survey$clean_up[survey$callsign == "KD3CCO"] <- TRUE
survey$clean_up[survey$callsign == "K3YV"] <- TRUE
survey$youth[survey$callsign == "KD3CCP"] <- TRUE
survey$food[survey$callsign == "KD3AQC"] <- TRUE

survey$name[survey$callsign == "KM3AJ"] <- "Gene Moore"
survey$name[survey$callsign == "K3YV"] <- "Woody Brem"
```

### Computers, networking, submitting logs

- Mike Coslo N3LI

### Safety Officer

- John Guss N3GU has served in this role in the past, but we need to have a second for when he is not on-site.

### Served Agency Official

- Brett Saylor W3SWL, Red Cross will be our official visitor (confirmed 2026-06-04)

## Teams

### Stations {#stations}

```{r}
#| echo: false
stations <- survey |>
  dplyr::filter(stations == TRUE) |>
  dplyr::select(name, callsign)

stations |>
  kableExtra::kbl(format = "html")
```

### Publicity {#pub-comm}

```{r}
#| echo: false
publicity <- survey |>
  dplyr::filter(info_table == TRUE |
                  invite_elected == TRUE |
                  youth == TRUE) |>
  dplyr::select(name, callsign)

publicity |>
  kableExtra::kbl(format = "html")
```

### Food & Drink {#food-comm}

```{r}
#| echo: false
food <- survey |>
  dplyr::filter(food == TRUE) |>
  dplyr::select(name, callsign)

food |>
  kableExtra::kbl(format = "html")
```

### Ed Activity {#ed-comm}

```{r}
#| echo: false
ed_activity <- survey |>
  dplyr::filter(ed_activity == TRUE) |>
  dplyr::select(name, callsign)

ed_activity |>
  kableExtra::kbl(format = "html")
```

### Set-up/Clean-up/Equipment {#set-up-comm}

As indicated by results from the [survey](survey.qmd).

```{r}
#| echo: false
setup_cleanup <- survey |>
  dplyr::filter(clean_up == TRUE) |>
  dplyr::select(name, callsign)

setup_cleanup |>
  kableExtra::kbl(format = "html")
```
