---
title: "Survey"
format:
  html:
    code-fold: true
    code-tools: true
    toc: true
params:
  update_data: false
  data_path: include/csv
  survey_data_fn: narc-fd-2026-survey.csv
  survey_sheet_fn: "Field Day 2026 volunteer sign-up (Responses)"
  survey_sheet_id: "15oLSzFPye2Cku6QkqsrxZ1c61SbjrDVrekQK0z55vTE"
---

## About

This page documents some of the steps in our planning process.

W3TM drafted and distributed on <DATE> a member survey using a Google Form.
Here are some of the preliminary results.

::: {.callout-note}

To reveal the code that generates the following outputs, select the 'Show All Code' item from the '</> Code' dropdown menu at upper right.

:::

## Set-up

We source some packages to make calls to their functions more convenient.

```{r}
library(ggplot2)
library(tibble)
library(dplyr)
knitr::opts_chunk$set(tidy = "styler")
```

## Gathering

The Google Form application saves the survey responses as a Google Sheet:

https://docs.google.com/forms/d/e/1FAIpQLScAu-pfcYEfVoUwy_xHOlA3KDA3ZfFuiYYJRorVdLNXfahjSQ/viewform?usp=header

```{r}
if (!dir.exists('csv')) {
  message("Creating missing `csv/`.")
  dir.create("csv")
}

update_figs = TRUE

full_survey_data_fn <- file.path("csv", params$survey_data_fn)

if (params$update_data) {
  options(gargle_oauth_email = Sys.getenv("GMAIL_ROG"))
  googledrive::drive_auth()
  
  new_fn <- file.path("csv", paste0(params$survey_data_fn))
  fd26 <- googlesheets4::gs4_find() |> dplyr::filter(stringr::str_detect(name, "Field Day 2026"))

  fd_2026 <- googlesheets4::read_sheet(ss = fd26$id, sheet = "Form Responses 1")
  x <- assertthat::assert_that(is_tibble(fd_2026))
  message("Data updated.")
  readr::write_csv(fd_2026, file = new_fn)
} else {
  if (!file.exists(full_survey_data_fn)) {
    warning("File not found: '", full_survey_data_fn, "'.")
    update_figs = FALSE
  } else {
    message("Using previously stored data.")
  }
}
```

Now, we load the downloaded CSV

```{r load-survey-data}
if (update_figs) {
  survey_resps <-
    readr::read_csv(full_survey_data_fn, show_col_types = FALSE)
}

names(survey_resps)
```

## Cleaning

Then we clean the data by renaming the variables.

```{r rename-variables}
survey_resps <- survey_resps |>
  dplyr::rename(
    timestamp = "Timestamp",
    name = "Your Name",
    callsign = "Callsign",
    phone = "Phone",
    email = "Email",
    attend = "Do you plan to attend NARC's Field Day 2025?",
    operate = "Do you plan to operate on Field Day?",
    overnight = "Are you a night owl and want to operate late into the night or camp out to snag some rare DX?",
    help_with = "I'm interested in helping with the following activities to promote Field Day and amateur radio to the public...",
    comments = "Comments or suggestions"
  )

names(survey_resps)[9] <- "modes"
```

Then we parse variables with multiple values, and conforming some values so that they are easier to visualize.

```{r recode-variables, tidy = "styler"}
survey_resps <- survey_resps |>
  # Change timestamp to proper date and time
  dplyr::mutate(timestamp = lubridate::mdy_hms(timestamp,
                                               tz = "America/New_York")) |>
  # Change values for 'attend' to make them more easily readable
  dplyr::mutate(when = attend) |>
  dplyr::mutate(
    when = case_when(
      when == "Yes, on Saturday June 27" ~ "sat",
      when == "Yes, on Sunday June 28" ~ "sun",
      when == "Yes, on Saturday June 27, Yes, on Sunday June 28" ~ "sat_sun",
      when == "Not sure yet" ~ "not_sure",
      when == "Sorry, not this year" ~ "no"
    )) |>
  # Change values for 'operate' to make them lower case
  dplyr::mutate(operate = tolower(operate)) |>
  # Change values for 'overnight'
  dplyr::mutate(overnight = dplyr::recode(
    overnight,
      'Yes, absolutely' = TRUE,
      'Heck no' = FALSE)) |>
  # Create new variable for each mode
  dplyr::mutate(
    phone = stringr::str_detect(modes, "Phone"),
    cw = stringr::str_detect(modes, "CW"),
    ft8 = stringr::str_detect(modes, "FT8/FT4"),
    varac = stringr::str_detect(modes, "VarAC"),
    fldigi = stringr::str_detect(modes, "fldigi"),
    js8call = stringr::str_detect(modes, "JS8Call"),
    sstv = stringr::str_detect(modes, "SSTV")
  ) |>
  # Create new variables for each volunteer role
  dplyr::mutate(
    pr = stringr::str_detect(help_with, "PR"),
    info_table = stringr::str_detect(help_with, "table"),
    satellite = stringr::str_detect(help_with, "satellite"),
    mode_expert = stringr::str_detect(help_with, "expert"),
    ed_activity = stringr::str_detect(help_with, "Educational"),
    invite_elected = stringr::str_detect(help_with, "elected"),
    youth = stringr::str_detect(help_with, "youth"),
    food = stringr::str_detect(help_with, "food"),
    clean_up = stringr::str_detect(help_with, "clean-up"),
    test_equipment = stringr::str_detect(help_with, "equipment")
  )

survey_resps$overnight[is.na(survey_resps$overnight)] <- FALSE
survey_resps$pr[is.na(survey_resps$pr)] <- FALSE
survey_resps$info_table[is.na(survey_resps$info_table)] <- FALSE
survey_resps$satellite[is.na(survey_resps$satellite)] <- FALSE
survey_resps$mode_expert[is.na(survey_resps$mode_expert)] <- FALSE
survey_resps$ed_activity[is.na(survey_resps$ed_activity)] <- FALSE
survey_resps$invite_elected[is.na(survey_resps$invite_elected)] <- FALSE
survey_resps$youth[is.na(survey_resps$youth)] <- FALSE
survey_resps$food[is.na(survey_resps$food)] <- FALSE
survey_resps$clean_up[is.na(survey_resps$clean_up)] <- FALSE
survey_resps$test_equipment[is.na(survey_resps$test_equipment)] <- FALSE
```

It will be easier if we make separate variables for attendance on Sat and Sun, so we do that now.

```{r}
survey_resps <- survey_resps |>
  dplyr::mutate(
    attend_sat = stringr::str_detect(when, "sat"),
    attend_sun = stringr::str_detect(when, "sun")
  ) |>
  dplyr::mutate(attend_any = (attend_sat | attend_sun))
```

We make all the callsigns uppercase for consistency.

```{r}
survey_resps <- survey_resps |>
  dplyr::mutate(callsign = toupper(callsign))
```

Finally, we export the cleaned file.

```{r}
readr::write_csv(survey_resps, file.path("csv", paste0("clean_", params$survey_data_fn)))
```

## Visualizing

<!-- As of `{r} Sys.time()`, we've had `{r} dim(survey_resps)[1]` responses. -->

### Attending and operating

Here are the number of respondents who plan to attend and their plans to operate.

```{r}
xtabs(formula = ~ when + operate, data = survey_resps)
```

```{r}
survey_resps |>
  dplyr::select(callsign, attend_sat, overnight, attend_sun) |>
  dplyr::filter(!is.na(attend_sat), !is.na(overnight), !is.na(attend_sun)) |>
  kableExtra::kbl(format = "html") |>
  kableExtra::kable_classic() |>
  kableExtra::column_spec(2, 
    color = ifelse(survey_resps$attend_sat == TRUE, "green", "red")) |>
  kableExtra::column_spec(4, 
    color = ifelse(survey_resps$attend_sun == TRUE, "green", "red")) |>
  kableExtra::column_spec(3, 
    color = ifelse(survey_resps$overnight == TRUE, "green", "red"))
```

### Modes

Here are respondents' interests by mode:

```{r}
attendees <- survey_resps |>
  dplyr::filter(attend_any == TRUE)

modes <- attendees |>
  dplyr::filter(
    !is.na(callsign),
    !is.na(phone),
    !is.na(cw),
    !is.na(ft8),
    !is.na(varac),
    !is.na(fldigi),
    !is.na(js8call),
    !is.na(sstv)
  ) |>
  dplyr::select(callsign, phone, cw, ft8, varac, fldigi, js8call, sstv)

modes |>
  kableExtra::kbl(format = "html") |>
  kableExtra::kable_classic() |>
  kableExtra::column_spec(column = 2, color = ifelse(modes$phone == TRUE, "green", "red")) |>
  kableExtra::column_spec(column = 3, color = ifelse(modes$cw == TRUE, "green", "red")) |>
  kableExtra::column_spec(column = 4, color = ifelse(modes$ft8 == TRUE, "green", "red")) |>
  kableExtra::column_spec(column = 5, color = ifelse(modes$varac == TRUE, "green", "red")) |>  
  kableExtra::column_spec(column = 6, color = ifelse(modes$fldigi == TRUE, "green", "red")) |>
  kableExtra::column_spec(column = 7, color = ifelse(modes$js8call == TRUE, "green", "red")) |>
  kableExtra::column_spec(column = 8, color = ifelse(modes$sstv == TRUE, "green", "red")) 

```

