---
title: "Power estimation"
format: html
params:
  sheet_url: "https://docs.google.com/spreadsheets/d/10F2JfQ3A6oFc3VFz_GTDg_t_ZwVtrC2EGjVt0kopYQU/edit?gid=0#gid=0"
  google_email: "nittany.amateur.radio.club@gmail.com"
  update_data: false
---

## About

This page documents estimations about power usage for Field Day.

## Setup

```{r}
library(googlesheets4)
```

```{r}
gs4_auth(email = params$google_email)
```

## Import

W3TM generated a Google Sheet with data for these estimates:

<https://docs.google.com/spreadsheets/d/10F2JfQ3A6oFc3VFz_GTDg_t_ZwVtrC2EGjVt0kopYQU/edit?gid=0#gid=0>

```{r}
#| label: import-google-sheet

if (params$update_data) {
  gs4_auth(email = params$google_email)
  power <- read_sheet(params$sheet_url)
  
  readr::write_csv(power, file = "csv/power-estimation.csv")
} else {
  message("Data not updated. Using stored copy")
}
```

```{r}
power <- readr::read_csv(file = "csv/power-estimation.csv", show_col_types = TRUE)
```

## Summarize

The modes summarized here include: `r unique(power$mode)`.

Power levels estimated for the modes are as follows:

```{r}
xtabs(~ mode + xmit_watts, data = power)
```

We're more likely to run 40W on FT8.

Duty cycles for these modes are as follows:

```{r}
xtabs(~ mode + duty_cycle, data = power)
```

The 0.5 duty cycle for FT8 and 0.3 duty cycle for phone assume pretty aggressive running on a frequency.
More realistic duty cycles are 0.25 for phone FT8.

Operating hours are estimated as follows:

```{r}
xtabs(~ op_hrs_ham, data = power)
```


## Scenario: Modest duty cycles + 12 hour operating

```{r}
power |>
  dplyr::filter(op_hrs_ham == 12,
                duty_cycle == .25) |>
  dplyr::select(mode, battery_Ah, op_hrs_battery, batt_24hrs)
```

This implies that we would need 1 30 Ah battery to run FT8 for the entire 24 hr period, and 1.7 (round to 2) 40 Ah batteries to run phone the entire 24 hour period.

## Scenario: Modest duty cycles + 18 hour operating

```{r}
power |>
  dplyr::filter(op_hrs_ham == 18,
                duty_cycle == .25) |>
  dplyr::select(mode, battery_Ah, op_hrs_battery, batt_24hrs)
```
We would need 2 40 Ah batteries for FT8 and 3 40 Ah batteries to run phone.

## Scenario: Aggressive duty cycles + 24 hour operating

```{r}
power |>
  dplyr::filter(op_hrs_ham == 24,
                duty_cycle > .25) |>
  dplyr::select(mode, duty_cycle, battery_Ah, op_hrs_battery, batt_24hrs)
```
Under an aggressive operating and duty cycle schedule, we'd need 3 40 Ah batteries to run FT8 and 5 40 Ah batteries to operate.

::: {.callout-important}
These scenarios do *not* estimate any impact of solar recharging.

However, since recharging really only helps beginning Sunday morning, the impact is only on the daylight hours on Sunday. 
:::

## Batteries available

The club does not own any batteries.

W3TM has the following:

- 1x 30 Ah
- 2x 40 Ah

So, W3TM could cover an FT8 and a phone station for Field Day under the modest operating scenario.

For more active operating scenarios, we would need to rely on recharging batteries Sunday morning, more batteries, or larger batteries than W3TM has available.


