---
title: "Survey"
format:
  html:
    code-fold: true
    code-tools: true
    toc: true
params:
  update_data: true
  survey_data_fn: narc-fd-2024-survey.csv
  survey_sheet_fn: "Field Day 2024 volunteer sign-up (Responses)"
---

## About

This page documents some of the steps in our planning process.

W3TM drafted and distributed on 2024-05-28 a member survey using a Google Form.
Here are some of the preliminary results.

::: {.callout-note}

To reveal the code that generates the following outputs, select the 'Show All Code' item from the '</> Code' dropdown menu at upper right.

:::

## Set-up

We source some packages to make calls to their functions more convenient.

```{r}
library(ggplot2)
knitr::opts_chunk$set(tidy = "styler")
```

## Gathering

The Google Form application saves the survey responses as a Google Sheet:

https://docs.google.com/spreadsheets/d/1Rr2kPK16v0tG-c8dm03gl3jqBNqB_DGyQtVcCVmFadg/edit?resourcekey#gid=283208367

```{r}
if (!dir.exists('csv')) {
  message("Creating missing `csv/`.")
  dir.create("csv")
}

update_figs = TRUE

full_survey_data_fn <- file.path("csv", params$survey_data_fn)

if (params$update_data) {
  options(gargle_oauth_email = Sys.getenv("GMAIL_ROG"))
  googledrive::drive_auth()
  
  new_fn <- file.path("csv", paste0("_", params$survey_data_fn))
  googledrive::drive_download(
    params$survey_sheet_fn,
    path = full_survey_data_fn,
    type = "csv",
    overwrite = TRUE
  )
  message("Data updated.")
} else {
  if (!file.exists(full_survey_data_fn)) {
    warning("File not found: '", full_survey_data_fn, "'.")
    update_figs = FALSE
  } else {
    message("Using previously stored data.")
  }
}
```

Now, we load the downloaded CSV

```{r load-survey-data}
if (update_figs) {
  survey_resps <-
    readr::read_csv(full_survey_data_fn, show_col_types = FALSE)
}

names(survey_resps)
```

## Cleaning

Then we clean the data by renaming the variables.

```{r rename-variables}
survey_resps <- survey_resps |>
  dplyr::rename(
    timestamp = "Timestamp",
    name = "Your Name",
    callsign = "Callsign",
    phone = "Phone",
    email = "Email",
    attend = "Do you plan to attend NARC's Field Day 2024?",
    operate = "Do you plan to operate on Field Day?",
    overnight = "Are you a night owl and want to operate late into the night or camp out to snag some rare DX?",
help_with = "I'm interested in helping with the following activities to promote Field Day and amateur radio to the public...",
comments = "Comments or suggestions"
  )

names(survey_resps)[9] <- "modes"
```

Then we parse variables with multiple values, and conforming some values so that they are easier to visualize.

```{r recode-variables, tidy = "styler"}
survey_resps <- survey_resps |>
  # Change timestamp to proper date and time
  dplyr::mutate(timestamp = lubridate::mdy_hms(timestamp, tz = "America/New_York")) |>
  # Change values for 'attend' to make them more easily readable
  dplyr::mutate(
    attend = dplyr::recode(
      attend,
        'Yes, on Saturday June 22' = "sat",
        'Yes, on Sunday June 23' = "sun",
        'Yes, on Saturday June 22, Yes, on Sunday June 23' = "sat_sun",
        'Not this year' = "no"
    )
  ) |>
  # Change values for 'operate' to make them lower case
  dplyr::mutate(operate = tolower(operate)) |>
  # Change values for 'overnight'
  dplyr::mutate(overnight = dplyr::recode(
    overnight,
      'Yes, absolutely' = TRUE,
      'Heck no' = FALSE)) |>
  # Create new variable for each mode
  dplyr::mutate(
    phone = stringr::str_detect(modes, "Phone"),
    cw = stringr::str_detect(modes, "CW"),
    ft8 = stringr::str_detect(modes, "FT8/FT4"),
    varac = stringr::str_detect(modes, "VarAC"),
    fldigi = stringr::str_detect(modes, "fldigi"),
    js8call = stringr::str_detect(modes, "JS8Call"),
    sstv = stringr::str_detect(modes, "SSTV")
  ) |>
  # Create new variables for each volunteer role
  dplyr::mutate(
    pr = stringr::str_detect(help_with, "PR"),
    info_table = stringr::str_detect(help_with, "table"),
    satellite = stringr::str_detect(help_with, "satellite"),
    mode_expert = stringr::str_detect(help_with, "expert"),
    ed_activity = stringr::str_detect(help_with, "Educational"),
    invite_elected = stringr::str_detect(help_with, "elected"),
    youth = stringr::str_detect(help_with, "youth"),
    food = stringr::str_detect(help_with, "food"),
    clean_up = stringr::str_detect(help_with, "clean-up"),
    test_equipment = stringr::str_detect(help_with, "equipment")
  )

survey_resps$overnight[is.na(survey_resps$overnight)] <- FALSE
survey_resps$pr[is.na(survey_resps$pr)] <- FALSE
survey_resps$info_table[is.na(survey_resps$info_table)] <- FALSE
survey_resps$satellite[is.na(survey_resps$satellite)] <- FALSE
survey_resps$mode_expert[is.na(survey_resps$mode_expert)] <- FALSE
survey_resps$ed_activity[is.na(survey_resps$ed_activity)] <- FALSE
survey_resps$invite_elected[is.na(survey_resps$invite_elected)] <- FALSE
survey_resps$youth[is.na(survey_resps$youth)] <- FALSE
survey_resps$food[is.na(survey_resps$food)] <- FALSE
survey_resps$clean_up[is.na(survey_resps$clean_up)] <- FALSE
survey_resps$test_equipment[is.na(survey_resps$test_equipment)] <- FALSE

```

It will be easier if we make separate variables for attendance on Sat and Sun, so we do that now.

```{r}
survey_resps <- survey_resps |>
  dplyr::mutate(
    attend_sat = stringr::str_detect(attend, "sat"),
    attend_sun = stringr::str_detect(attend, "sun")
  ) |>
  dplyr::mutate(attend_any = (attend_sat | attend_sun))
```

We make all the callsigns uppercase for consistency.

```{r}
survey_resps <- survey_resps |>
  dplyr::mutate(callsign = toupper(callsign))
```

Finally, we export the cleaned file.

```{r}
readr::write_csv(survey_resps, file.path("csv", paste0("clean_", params$survey_data_fn)))
```

## Visualizing

<!-- As of `{r} Sys.time()`, we've had `{r} dim(survey_resps)[1]` responses. -->

### Attending and operating

Here are the number of respondents who plan to attend and their plans to operate.

```{r}
xtabs(formula = ~ attend + operate, data = survey_resps)
```
```{r}
survey_resps |>
  dplyr::select(callsign, attend_sat, overnight, attend_sun) |>
  kableExtra::kbl(format = "html") |>
  kableExtra::kable_classic() |>
  kableExtra::column_spec(2, 
    color = ifelse(survey_resps$attend_sat == TRUE, "green", "red")) |>
  kableExtra::column_spec(4, 
    color = ifelse(survey_resps$attend_sun == TRUE, "green", "red")) |>
  kableExtra::column_spec(3, 
    color = ifelse(survey_resps$overnight == TRUE, "green", "red"))
```

<!-- #### Saturday -->

<!-- ```{r} -->
<!-- survey_resps |> -->
<!--   dplyr::select(callsign, attend_sat) |> -->
<!--   dplyr::filter(attend_sat == TRUE) |> -->
<!--     knitr::kable(format = 'html') -->
<!-- ``` -->

<!-- #### Sunday -->

<!-- ```{r} -->
<!-- survey_resps |> -->
<!--   dplyr::select(callsign, attend_sun) |> -->
<!--   dplyr::filter(attend_sun == TRUE) |> -->
<!--     knitr::kable(format = 'html') -->
<!-- ``` -->

<!-- #### Overnight -->

<!-- Here are respondents' plans to operate overnight: -->

<!-- ```{r} -->
<!-- xtabs(formula = ~ overnight, data = survey_resps) -->

<!-- survey_resps |> -->
<!--   dplyr::select(callsign, overnight) |> -->
<!--   dplyr::filter(overnight == TRUE) |> -->
<!--     knitr::kable(format = 'html') -->

<!-- ``` -->

### Modes

Here are respondents' interests by mode:

```{r}
attendees <- survey_resps |>
  dplyr::filter(attend_any == TRUE)

attendees |>
  dplyr::select(callsign, phone, cw, ft8, varac, fldigi, js8call, sstv) |>
  kableExtra::kbl(format = "html") |>
  kableExtra::kable_classic() |>
  kableExtra::column_spec(2, 
    color = ifelse(attendees$phone == TRUE, "green", "red")) |>
  kableExtra::column_spec(3,
    color = ifelse(attendees$cw == TRUE, "green", "red")) |>
  kableExtra::column_spec(4,
    color = ifelse(attendees$ft8 == TRUE, "green", "red")) |>
  kableExtra::column_spec(5,
    color = ifelse(attendees$varac == TRUE, "green", "red")) |>
  kableExtra::column_spec(6,
    color = ifelse(attendees$fldigi == TRUE, "green", "red")) |>
  kableExtra::column_spec(7,
    color = ifelse(attendees$js8call == TRUE, "green", "red")) |>
  kableExtra::column_spec(8,
    color = ifelse(attendees$sstv == TRUE, "green", "red"))

```


<!-- #### Phone -->

<!-- ```{r} -->
<!-- xtabs(formula = ~ phone, data = survey_resps) -->

<!-- survey_resps |> -->
<!--   dplyr::select(callsign, phone) |> -->
<!--   dplyr::filter(phone == TRUE) |> -->
<!--     knitr::kable(format = 'html') -->
<!-- ``` -->

<!-- #### CW -->

<!-- ```{r} -->
<!-- xtabs(formula = ~ cw, data = survey_resps) -->

<!-- survey_resps |> -->
<!--   dplyr::select(callsign, cw) |> -->
<!--   dplyr::filter(cw == TRUE) |> -->
<!--     knitr::kable(format = 'html') -->
<!-- ``` -->

<!-- #### FT8/FT4 -->

<!-- ```{r} -->
<!-- xtabs(formula = ~ ft8, data = survey_resps) -->

<!-- survey_resps |> -->
<!--   dplyr::select(callsign, ft8) |> -->
<!--   dplyr::filter(ft8 == TRUE) |> -->
<!--     knitr::kable(format = 'html') -->
<!-- ``` -->

<!-- #### VarAC -->

<!-- ```{r} -->
<!-- xtabs(formula = ~ varac, data = survey_resps) -->

<!-- survey_resps |> -->
<!--   dplyr::select(callsign, varac) |> -->
<!--   dplyr::filter(varac == TRUE) |> -->
<!--     knitr::kable(format = 'html') -->
<!-- ``` -->

<!-- #### Fldigi (e.g., PSK31) -->

<!-- ```{r} -->
<!-- xtabs(formula = ~ fldigi, data = survey_resps) -->

<!-- survey_resps |> -->
<!--   dplyr::select(callsign, fldigi) |> -->
<!--   dplyr::filter(fldigi == TRUE) |> -->
<!--     knitr::kable(format = 'html') -->
<!-- ``` -->

<!-- #### JS8Call -->

<!-- ```{r} -->
<!-- xtabs(formula = ~ js8call, data = survey_resps) -->

<!-- survey_resps |> -->
<!--   dplyr::select(callsign, js8call) |> -->
<!--   dplyr::filter(js8call == TRUE) |> -->
<!--     knitr::kable(format = 'html') -->
<!-- ``` -->

<!-- #### SSTV -->

<!-- ```{r} -->
<!-- xtabs(formula = ~ sstv, data = survey_resps) -->

<!-- survey_resps |> -->
<!--   dplyr::select(callsign, sstv) |> -->
<!--   dplyr::filter(sstv == TRUE) |> -->
<!--     knitr::kable(format = 'html') -->
<!-- ``` -->

### Volunteering

And here are respondents' interests in volunteering:

```{r}
volunteers <- survey_resps |>
  dplyr::select(callsign, pr, info_table, satellite, mode_expert,
    ed_activity, invite_elected, youth, food, clean_up, test_equipment)

volunteers |>
  kableExtra::kbl(format = "html") |>
  kableExtra::kable_classic() |>
  kableExtra::column_spec(2, 
    color = ifelse(volunteers$pr == TRUE, "green", "red")) |>
  kableExtra::column_spec(3,
    color = ifelse(volunteers$info_table == TRUE, "green", "red")) |>
  kableExtra::column_spec(4,
    color = ifelse(volunteers$satellite == TRUE, "green", "red")) |>
  kableExtra::column_spec(5,
    color = ifelse(volunteers$mode_expert == TRUE, "green", "red")) |>
  kableExtra::column_spec(6,
    color = ifelse(volunteers$ed_activity == TRUE, "green", "red")) |>
  kableExtra::column_spec(7,
    color = ifelse(volunteers$invite_elected == TRUE, "green", "red")) |>
  kableExtra::column_spec(8,
    color = ifelse(volunteers$youth == TRUE, "green", "red")) |>
  kableExtra::column_spec(9,
    color = ifelse(volunteers$food == TRUE, "green", "red")) |>
  kableExtra::column_spec(10,
    color = ifelse(volunteers$clean_up == TRUE, "green", "red")) |>
  kableExtra::column_spec(11,
    color = ifelse(volunteers$test_equipment == TRUE, "green", "red"))

```

<!-- #### PR -->

<!-- ```{r} -->
<!-- xtabs(formula = ~ pr, data = survey_resps) -->

<!-- survey_resps |> -->
<!--   dplyr::select(callsign, pr) |> -->
<!--   dplyr::filter(pr == TRUE) |> -->
<!--     knitr::kable(format = 'html') -->
<!-- ``` -->

<!-- #### Info table -->

<!-- ```{r} -->
<!-- xtabs(formula = ~ info_table, data = survey_resps) -->

<!-- survey_resps |> -->
<!--   dplyr::select(callsign, info_table) |> -->
<!--   dplyr::filter(info_table == TRUE) |> -->
<!--     knitr::kable(format = 'html') -->
<!-- ``` -->

<!-- #### Satellite QSO -->

<!-- ```{r} -->
<!-- xtabs(formula = ~ satellite, data = survey_resps) -->

<!-- survey_resps |> -->
<!--   dplyr::select(callsign, satellite) |> -->
<!--   dplyr::filter(satellite == TRUE) |> -->
<!--     knitr::kable(format = 'html') -->
<!-- ``` -->

<!-- #### Mode 'expert' -->

<!-- ```{r} -->
<!-- xtabs(formula = ~ mode_expert, data = survey_resps) -->

<!-- survey_resps |> -->
<!--   dplyr::select(callsign, mode_expert) |> -->
<!--   dplyr::filter(mode_expert == TRUE) |> -->
<!--     knitr::kable(format = 'html') -->
<!-- ``` -->

<!-- #### Educational activity -->

<!-- ```{r} -->
<!-- xtabs(formula = ~ ed_activity, data = survey_resps) -->

<!-- survey_resps |> -->
<!--   dplyr::select(callsign, ed_activity) |> -->
<!--   dplyr::filter(ed_activity == TRUE) |> -->
<!--     knitr::kable(format = 'html') -->
<!-- ``` -->

<!-- #### Invitations to elected officials -->

<!-- ```{r} -->
<!-- xtabs(formula = ~ invite_elected, data = survey_resps) -->

<!-- survey_resps |> -->
<!--   dplyr::select(callsign, invite_elected) |> -->
<!--   dplyr::filter(invite_elected == TRUE) |> -->
<!--     knitr::kable(format = 'html') -->
<!-- ``` -->

<!-- #### Invitations to youth groups -->

<!-- ```{r} -->
<!-- xtabs(formula = ~ youth, data = survey_resps) -->

<!-- survey_resps |> -->
<!--   dplyr::select(callsign, youth) |> -->
<!--   dplyr::filter(youth == TRUE) |> -->
<!--     knitr::kable(format = 'html') -->
<!-- ``` -->

<!-- #### Food & Drink -->

<!-- ```{r} -->
<!-- xtabs(formula = ~ food, data = survey_resps) -->

<!-- survey_resps |> -->
<!--   dplyr::select(callsign, food) |> -->
<!--   dplyr::filter(food == TRUE) |> -->
<!--     knitr::kable(format = 'html') -->
<!-- ``` -->

<!-- #### Clean-up -->

<!-- ```{r} -->
<!-- xtabs(formula = ~ clean_up, data = survey_resps) -->

<!-- survey_resps |> -->
<!--   dplyr::select(callsign, clean_up) |> -->
<!--   dplyr::filter(clean_up == TRUE) |> -->
<!--     knitr::kable(format = 'html') -->
<!-- ``` -->

<!-- #### Test equipment & software -->

<!-- ```{r} -->
<!-- xtabs(formula = ~ test_equipment, data = survey_resps) -->

<!-- survey_resps |> -->
<!--   dplyr::select(callsign, test_equipment) |> -->
<!--   dplyr::filter(test_equipment == TRUE) |> -->
<!--     knitr::kable(format = 'html') -->
<!-- ``` -->

<!-- #### Comments -->

<!-- And here are the comments: -->

<!-- ```{r} -->
<!-- survey_resps |> -->
<!--   dplyr::select(callsign, comments) |> -->
<!--   dplyr::filter(!is.na(comments)) |> -->
<!--   knitr::kable(format = 'html') -->
<!-- ``` -->

## Observations

- We have about half a dozen attendees who want to operate on Saturday and a larger group on Sunday.
- W3TM will have some company (W3EDP and KM4LAO) late at night or overnight.
- We have a number of operators interested in digital (FT8, fldigi, and JS8Call) modes.
- We should have 5-10 helpers to assist with strike/tear-down.
